ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-02 paper/wish/wsc15paper.tex
corrections

The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions. Specifically, this mapping begins with $A_0 = \{1,\ldots,k\}$,
$P_0=P^*$, 
and finds the first time $\tau_1$ that $q'_{tx}(A_0)$ falls above the threshold $P_0$,
or below the threshold $c$.
If the first case occurs, the alternative with the largest $q'_{\tau_1,x}(A_0)$ is selected as the best.
If the second case occurs, the alternative with the smallest
$q'_{\tau_1,x}(A_0)$ is eliminated, resulting in a new set $A_1$, a new selection threshold 
$P_1$ is calculated from $P_0$ and the eliminated alternative's value of $q'_{\tau_1,x}(A_0)$, and the process continues.
This process is repeated until an alternative is selected as the best.
Call this mapping $h$, so that the BIZ selection decision is
$h\left(\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right)$.

>>>>

The third one maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions. Specifically, this mapping begins with $A_0 = \{1,\ldots,k\}$,
$P_0=P^*$, 
and finds the first time $\tau_1$ that $q'_{tx}(A_0)$ falls above the threshold $P_0$,
or below the threshold $c$.
If the first case occurs, the alternative with the largest $q'_{\tau_1,x}(A_0)$ is selected as the best.
If the second case occurs, the alternative with the smallest
$q'_{\tau_1,x}(A_0)$ is eliminated, resulting in a new set $A_1$, a new selection threshold 
$P_1$ is calculated from $P_0$ and the eliminated alternative's value of $q'_{\tau_1,x}(A_0)$, and the process continues.
This process is repeated until an alternative is selected as the best.
Call this mapping $h$, so that the BIZ selection decision is
$h\left(\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right)$.
